Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-02 .output/_tex/manuscript.tex
fix wrong caption (from Yoel's comment)

\caption{\label{fig-model-prevalences-with-ipsi}Comparison of the
computed and observed prevalences for scenarios that illustrate the
model's capability of accounting for the correlation between ipsi- and
contralateral involvement. We show three scenarios where we consider the
joint involvement of contralateral LNL II together with different
ipsilateral involvements: 1) the ipsilateral neck shows no involvement
in blue (LNLs I to V are healthy, LNL VII is unspecified because data on
it is missing for some patients), 2) where ipsilateral LNL II is
involved in orange (LNLs I, III, IV, and V are healthy), and 3) where
ipsilateral LNLs II and III are involved in orange (LNLs I, IV, and V
are healthy). These two scenarios are plotted for all combinations of
T-category (early in top row, advanced in bottom row) and tumor
lateralization (lateralized in left column, extending over mid-sagittal
line in the right column).}

>>>>

\caption{\label{fig-model-prevalences-with-ipsi}Comparison of the
computed and observed prevalences for scenarios that illustrate the
model's capability of accounting for the correlation between ipsi- and
contralateral involvement. We show three scenarios where we consider the
joint involvement of contralateral LNL II together with different
ipsilateral involvements: 1) the ipsilateral neck shows no involvement
in green (LNLs I to V are healthy, LNL VII is unspecified because data
on it is missing for some patients), 2) where ipsilateral LNL II is
involved in orange (LNLs I, III, IV, and V are healthy), and 3) where
ipsilateral LNLs II and III are involved in red (LNLs I, IV, and V are
healthy). These three scenarios are plotted for all combinations of
T-category (early in top row, advanced in bottom row) and tumor
lateralization (lateralized in left column, extending over mid-sagittal
line in the right column).}
